---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# HeFTy.SmoothR

<!-- badges: start -->
  [![R-CMD-check](https://github.com/joelpadgett/HeFTy_SmoothR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/joelpadgett/HeFTy_SmoothR/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

Density plots derived from HeFTy inverse thermal history models as used in 
Padgett et al. (in press) and Johns-Buss et al. (submitted). 


## Prerequisites
You must have R installed on your system (see http://r-project.org). To install 
`HeFTy.SmoothR` from CRAN, type the following code at the R command line prompt:

```{r echo=TRUE, eval=FALSE}
# install.packages("remotes") # install if needed
remotes::install_github("padgett/HeFTy_SmoothR")
```

The format requirements for the import data are described in the detailed 
walkthrough:
```{r echo=TRUE, eval=FALSE}
vignette('hefty_smoothr', package = "HeFTy_SmoothR")
```

The following code provides a minimal working example to demonstrate the import 
and plotting of the data:


```{r demo, warning=FALSE,message=FALSE}
library("HeFTy.SmoothR")
library(ggplot2)

# load example data
path2myfile <- system.file("s14MM_v1.xlsx", package = "HeFTy.SmoothR") # example data
tT_paths <- read_hefty_xlsx(path2myfile)

plot_path_density_filled(tT_paths) +
  labs(
    title = "Kernel density of t-T paths",
    caption = "data from Padgett et al. (in press)",
    x = "Time (Ma)",
    y = bquote("Temperature (" * degree * "C)")
  ) +
  coord_cartesian(expand = FALSE) +
  scale_x_continuous(transform = "reverse", position = "top") +
  scale_y_continuous(transform = "reverse") +
  guides(fill = "none")
```

## Documentation
The detailed documentation can be found at

```{r echo=TRUE, eval=FALSE}
vignette('hefty_smoothr', package = "HeFTy.SmoothR")
```

## Authors
Joel Padgett (<joel.padgett@ucalgary.ca>)

Tobias Stephan (<tstephan@lakeheadu.ca>)

## Citation
If you use this package in your research, please cite the following:

Padgett, J., Enkelmann, E., Kellett, D., Moynihan, D., and Stephan, T. 
"Cenozoic exhumation and fault reactivation in southeastern Yukon constrained 
by low-temperature thermochronology". *Canadian Journal of Earth Sciences* (in press). 
DOI: 10.1139/cjes-2024-0147.

## Feedback, issues, and contributions

We welcome feedback, suggestions, issues, and contributions! If you have
found a bug, please file it
[here](https://github.com/padgett/HeFTy_SmoothR/issues) with minimal code to
reproduce the issue.


## License
MIT License
